### 2021-01-10 paper/sections/design.tex
third revision

We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of {\color{revise2} $ \hat{s}_{ic} $}. For a reference compression quality level $ c_{\rm ref} $, the compressed file size is {\color{revise2} $ \hat{s}_{\rm ref} $}. Besides, the input image from a specific scenery usually belongs to a particular contextual group~\cite{mcdnn}. For example, in the daytime, the input images are expected to have a bright background, while nighttime images are usually gray-scaled thermal images. Therefore, the agent in one scenery does not need to know all the contextual features in all ``sceneries''. We formulate this as contextual group $ \mathcal{X} $.
%This contextual grouping concept is also discussed in~\cite{mcdnn}.

@@

{\color{revise3} We start by giving some basics on Markov decision processes (MDPs) \cite{MDP}, which is represented by a tuple $<S,C,P,R,\gamma>$, where $S$ denotes a set of possible states $s$, $C$ a set of feasible actions $c$, $P$ the set of state transition probabilities, $R$ a reward function, and $\gamma$ a discount factor. We formulate the feature extractor's output  $ s = \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. We use $P_{ss'}^{c} = P \big[s' \mid s, c = \pi(s) \big]$ to denote the state transition probability from state $s$ to $s'$, where $\pi$ is a compression strategy mapping state to actions. We therefore obtain a sequence of states and actions $\{ s_1,c_1,s_2,...,c_{t-1},s_t \}$, and this formulation is a MDP.}

{\color{revise3} The goal of the agent is to interact with the emulator environment $ \{\mathcal{X}, M\} $ by selecting actions in a way that maximises future reward $R$. We define the future discounted reward at time t as $R_t = \sum_{\hat{t}=t}^{T'} \gamma^{\hat{t}-t}r_{\hat{t}}$ , where $T'$ is the step at which the task terminates. In our design, a compression task only has one step, detailed discussed in \ref{RL Design}}.

{\color{revise3} We denote the optimal \emph{action-value function} as the maximum expected reward $ Q^{*}(\mathcal{E}(f_t), c; \theta) = \max_{\pi} \mathbb{E} \big[R_t \mid s_t=s,c_t=c,\pi\big]$ to learn the optimal compression strategy $\pi$, where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. The optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $. Also, the optimal action-value function obeys an important identity known as the Bellman equation, and the optimal strategy is to select the action $c'$ maximising the expected value of $r + \gamma Q^{*}(s', c'; \theta) $ \cite{DQN}.}

@@

In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Baidu_choices1.pdf}}
		\centerline{(a) Baidu Vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Facepp_choices1.pdf}}
		\centerline{(b) Face++}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Amazon_choices1.pdf}}
		\centerline{(c) Amazon Rekognition}
	\end{minipage}		
	\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different cloud services}}
	\label{fig: quality_chosen}
}
\vspace{-0.2cm} 
\end{figure*}
%\vspace{-0.3cm}
%\begin{figure}[!t]
%	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
%	\label{fig: quality_chosen}
%	% \vspace{-0.3cm}
%\end{figure}

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
		\centerline{(a) ImageNet images}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.48\linewidth}
		\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
		\centerline{(b) FLIR images}
	\end{minipage}	
    \caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
	\label{fig: dataset_change}
}
\vspace{-0.1cm} 
\end{figure*}

>>>>

We also denote JPEG input images as $ f_{ic} = J(x_i, c) $ that for an input image $ x_i $ and a given compression quality level $ c $, and it outputs a compressed file $ f_{ic} $ at the size of {\color{revise2} $ \hat{s}_{ic} $}. For a reference compression quality level $ c_{\rm ref} $, the compressed file size is {\color{revise2} $ \hat{s}_{\rm ref} $}. {\color{revise3}Besides JPEG compression method, our framework is applicative for different image compression techniques, both traditional compression methods \cite{jpeg,webp,hevc,vvc} and neural network-based learned compression methods \cite{endtoend1,endtoend2,endtoend3,endtoend4}, which all have an optional compression level (rate-distortion tradeoff parameter).}

Besides, the input image from a specific scenery usually belongs to a particular contextual group~\cite{mcdnn}. For example, in the daytime, the input images are expected to have a bright background, while nighttime images are usually gray-scaled thermal images. Therefore, the agent in one scenery does not need to know all the contextual features in all ``sceneries''. We formulate this as contextual group $ \mathcal{X} $.
%This contextual grouping concept is also discussed in~\cite{mcdnn}.

@@

{\color{revise3} We start by giving some basics on Markov decision processes (MDPs) \cite{MDP}, which is represented by a tuple $<S,C,P,R,\gamma>$, where $S$ denotes a set of possible states $s$, $C$ a set of feasible actions $c$, $P$ the set of state transition probabilities, $R$ a future reward function, and $\gamma$ a discount factor. We formulate the feature extractor's output  $ s = \mathcal{E}(J(\mathcal{X}, c)) $ as \emph{states} and the compression quality level $ c $ as discrete \emph{actions}. In our system, to accelerate training, we define 10 discrete actions to indicate 10 compression quality levels of JPEG ranging from $ 5, 15, ...,95 $. In our design, a compression task only has one step, detailed discussed in \ref{RL Design}. Therefore the next state and current action are only related to the current state, not to the historical states (i.e., $P_{s_{t}s_{t+1}}^{c_{t}} = P [s_{t+1} \mid s_{t}, c_t , s_{t-1}, c_{t-1},... ] = P [s_{t+1} \mid s_{t}, c_t ] ; P [ a_{t} \mid s_{1},s_{2},...,s_{t},a_{1},a_{2},...a_{t-1}] = P [ a_{t} \mid s_{t} ]$ ), satisfying Markov property.}

%Therefore the next state is only  We use $P_{ss'}^{c} = P \big[s' \mid s, c = \pi(s) \big]$ to denote the state transition probability from state $s$ to $s'$, where $\pi$ is a compression strategy mapping state to actions.  
%
%We therefore obtain a sequence of states and actions $\{ s_1,c_1,s_2,...,c_{t-1},s_t \}$, and this formulation is a MDP.}

{\color{revise3} The goal of the agent is to interact with the emulator environment $ \{\mathcal{X}, M\} $ by selecting actions in a way that maximizes future reward $R$. We define the future discounted reward at time t as $R_t = \sum_{\hat{t}=t}^{T'} \gamma^{\hat{t}-t}r_{\hat{t}}$ , where $T'$ is the step at which the task terminates.}{\color{revise3} We denote the optimal \emph{action-value function} as the maximum expected reward $ Q(\mathcal{E}(f_t), c; \theta) = \max_{\pi} \mathbb{E} \big[R_t \mid s_t=s,c_t=c,\pi\big]$ to learn the optimal compression strategy $\pi$, where $ \theta $ indicates the parameters of the Deep Q-learning Network $ \phi $. The optimal compression quality level at time $ t $ as $  c_t = {\rm argmax}_cQ(\mathcal{E}(f_t), c; \theta) $. Also, the optimal action-value function obeys an important identity known as the Bellman equation, and the optimal strategy is to select the action $c'$ maximising the expected value of $r + \gamma Q(s_{t+1}, c'; \theta) $ \cite{DQN}.}

@@

%In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_i(\theta_i) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_i - Q(s, c; \theta_i)\big)^2 \Big] $ that changes at each iteration $ i $ where {\color{revise2} state $ s = \mathcal{E}(f_i) $} and target $ y_i = \mathbb{E}_{s' \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s', c'; \theta_{i-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_i $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action. 
In such reinforcement learning formulation, the training phase is to minimize the loss function $ L_t(\theta_t) = \mathbb{E}_{s, c \sim \rho (\cdot)}\Big[\big(y_t - Q(s, c; \theta_t)\big)^2 \Big] $ that changes at each iteration $ t $ where {\color{revise2} state $ s = \mathcal{E}(f_t) $} and target $ y_t = \mathbb{E}_{s^{t+1} \sim \{\mathcal{X}, M\}} \big[ r + \gamma \max_{c'} Q(s_{t+1}, c'; \theta_{t-1}) \mid s, c \big] $. Especially, $ r $ is the reward feedback, and $ \rho(s, c) $ is a probability distribution over {\color{revise2} state} \iffalse sequences \fi $ s $ and the compression quality level $ c $~\cite{DQN}. When minimizing the distance of \emph{action-value function}'s output $ Q(\cdot) $ and target $ y_t $, the \emph{action-value function} $ Q(\cdot) $ outputs a more accurate estimation of an action.

@@

\begin{figure*}[!t]
{\color{revise}
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Baidu_choices1.pdf}}
		\centerline{(a) Baidu Vision}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Facepp_choices1.pdf}}
		\centerline{(b) Face++}
	\end{minipage}
	\hfill
	\begin{minipage}[t]{0.32\linewidth}
		\centerline{\includegraphics[width=4.8cm]{figures/ImageNet_Amazon_choices1.pdf}}
		\centerline{(c) Amazon Rekognition}
	\end{minipage}		
	\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different cloud services}}
	\label{fig: quality_chosen}
}
%\vspace{-0.2cm} 
\end{figure*}
%\vspace{-0.3cm}
%\begin{figure}[!t]
%	\includegraphics[width=0.8\linewidth]{figures/quality_chosen.pdf}
%	\caption{Histogram of RL agent's best compression quality level selection for different cloud services}
%	\label{fig: quality_chosen}
%	% \vspace{-0.3cm}
%\end{figure}

\begin{figure*}[!t]
	{\color{revise}
		\begin{minipage}[t]{0.48\linewidth}
			\centerline{\includegraphics[width=7cm]{figures/ImageNet_Baidu_choices.pdf}}
			\centerline{(a) ImageNet images}
		\end{minipage}
		\hfill
		\begin{minipage}[t]{0.48\linewidth}
			\centerline{\includegraphics[width=7cm]{figures/FLIR_Baidu_choices.pdf}}
			\centerline{(b) FLIR images}
		\end{minipage}	
		\caption{\textcolor{revise}{Histogram of RL agent's best compression quality level selection for different scenery image inputs}}
		\label{fig: dataset_change}
	}
	\vspace{-0.2cm} 
\end{figure*}

@@

### 2021-01-10 paper/sections/evaluation.tex
third revision

	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_q75.jpeg}}
		\centerline{(2a) Origin Image (Q=75)}
		\centerline{Baidu prediction \ = \ [``cake'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_q65.jpeg}}
		\centerline{(2b) AdaCompress (choose Q=65)}
		\centerline{Baidu prediction \ = \ [``cake'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_deepn.jpeg}}
		\centerline{(2c) DeepN-JPEG}
		\centerline{Baidu prediction \ = \ [``fossil'']}
	\end{minipage}
	%	\vspace{0.2cm}
	\caption{Comparative compressed images of DeepN-JPEG and AdaCompress}
	\label{fig: compare_image}
\end{figure*}

@@

\subsection{Applicability for Different Image Compression Methods}

{\color{revise3} In our experiment, we choose the JPEG compression method as the compression framework. Furthermore, our framework is applicative for different image compression techniques, both traditional compression methods and neural network-based learned compression methods. Existing traditional compression methods all have an optional compression level, e.g., JPEG and WebP have the compression quality level, H.265/HEVC \cite{hevc} and H.266/VVC \cite{vvc} have the quantization parameter (QP). Neural network-based learned image compression is a Lagrangian multiplier-based rate-distortion optimization, which commonly has a tradeoff parameter that controls the rate-distortion tradeoff \cite{endtoend1,endtoend2,endtoend3,endtoend4}. Different values are corresponding to different bit rates. We can regard this tradeoff parameter as the compression level. These different compression techniques all can flexibly take a compression level as the input.}

>>>>

	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_q75.jpeg}}
		\centerline{(2a) Origin Image (Q=75)}
		\centerline{Baidu prediction \ = \ [``cake'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.2\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_q65.jpeg}}
		\centerline{(2b) AdaCompress (choose Q=65)}
		\centerline{Baidu prediction \ = \ [``cake'']}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centerline{\includegraphics[width=4.0cm,trim=0 0 0 0,clip ]{figures/cake_deepn.jpeg}}
		\centerline{(2c) DeepN-JPEG}
		\centerline{Baidu prediction \ = \ [``fossil'']}
	\end{minipage}
	%	\vspace{0.2cm}
	\caption{Comparative compressed images of DeepN-JPEG and AdaCompress}
	\label{fig: compare_image}
\vspace{-0.2cm}
\end{figure*}

@@

%\subsection{Applicability for Different Image Compression Methods}
%
%{\color{revise3} In our experiment, we choose the JPEG compression method as the compression framework. Furthermore, our framework is applicative for different image compression techniques, both traditional compression methods \cite{jpeg,webp,hevc,vvc} and neural network-based learned compression methods \cite{endtoend1,endtoend2,endtoend3,endtoend4}, which all have an optional compression level ( we can use this as the agent's action in our solution). 
%	
%Existing traditional compression methods all have an optional compression level, e.g., JPEG and WebP have the compression quality level, H.265/HEVC \cite{hevc} and H.266/VVC \cite{vvc} have the quantization parameter (QP). Neural network-based learned image compression is a Lagrangian multiplier-based rate-distortion optimization, which commonly has a tradeoff parameter that controls the rate-distortion tradeoff \cite{endtoend1,endtoend2,endtoend3,endtoend4}. Different values are corresponding to different bit rates. We can regard this tradeoff parameter as the compression level. These different compression techniques all can flexibly take a compression level as the input.}
